Local Spectral Clustering of Density Upper Level Sets

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates -- almost done with main text

\begin{theorem}
  \label{thm: consistent_recovery_of_density_clusters}
  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
  such that if  
  \begin{equation}
    \label{eqn: kappa_ub}
    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
  \end{equation}
  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
\end{theorem}

\begin{remark}
  We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
  density cluster $\Cset$ in the sense of \eqref{eqn:
    consistent_density_cluster_recovery} only when we can guarantee a very small
  fraction of points will be misclassified. This strong condition is the price
  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
\end{remark}

\begin{remark}
  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
  behavior of PPR in this regime. Although the restriction to a kernel
  function fixed in $n$ is standard for spectral clustering theory
  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
  this is merely looseness in our upper bounds.  
\end{remark}

\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
changed this $\epsilon$ to $\varepsilon$.}

\subsection{Approximate PPR vector} 
In practice, exactly solving \eqref{eqn:
  ppr_vector} may be too computationally expensive. To address this limitation,
\citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
(aPPR), which we will denote by \smash{$\pbf^{(\varepsilon)}$}. We refer the
curious reader to \citet{andersen2006} for a formal algorithmic definition of
the aPPR vector, and limit ourselves to highlighting a few salient points: the
aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time,
while satisfying the following uniform error bound: 
\begin{equation}
\label{eqn: appr_error}
\textrm{for all $u \in V$}, \quad \pbf(u) - \varepsilon \Dbf_{uu}\leq
\pbf^{(\varepsilon)}(u) \leq \pbf(u).  
\end{equation}
Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
formally state and prove this in Corollary~\ref{cor: appr} in 
the appendix.

@@

\paragraph{Normalized cut.} We start with a finite sample upper bound on the
normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
  $\epsilon > 0$, if 
  \begin{equation}
    \label{eqn: conductance_sample_complexity}
    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
  \end{equation}
  then with probability at least $1-\delta$, for a universal constant $c_1 > 0$,
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
  \end{equation}
\end{theorem}

\begin{remark}
  \label{rmk: diameter}
  Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
    conductance_upper_bound}, in contrast to the condition number
  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This
  reflects established wisdom regarding spectral partitioning
  algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
  to the density clustering setting. It suggests that if the diameter $\rho$ is
  large, PPR may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is
  sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized
  cut in $G_{n,r}$. This intuition will be supported by simulations in Section
  \ref{sec: experiments}. 
\end{remark}

\paragraph{Mixing time.} For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
$\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write  
$$
q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
$$
for the $t$-step transition probability of the lazy random walk over $G[S]$
originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
for the stationary distribution of this random walk.  (As
$\Wbf_S$ is the transition matrix of a lazy random walk, 
it is well-known that a unique stationary distribution exists and is given by 
\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where we write $\Dbf_S$ for the  
degree matrix of $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
\begin{equation}
\label{eqn: mixing_time}
\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)}
  {\pi(u)} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}. 
\end{equation}
Next, we give an asymptotic (in the number of vertices $n$) upper bound on
$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.

@@

\begin{remark}
  The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
  play an important role in proving the upper bound of Theorem \ref{thm:
    mixing_time_upper_bound}. There is some interdependence between $L$ and
  $\sigma,\rho$, which might lead one to hope that \ref{asmp: embedding} is
  non-essential. However, it is not possible to eliminate condition \ref{asmp:
    embedding} without incurring an additional factor of at least
  $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for
  instance, when $\Csig$ is a dumbbell-like set consisting of two balls of
  diameter $\rho$ linked by a cylinder of radius
  $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
  develop theory regarding bi-Lipschitz deformations of convex sets, wherein it
  is observed that star-shaped sets as well as half-moon shapes of the type we
  consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding}
  for reasonably small values of $L$. 
\end{remark}

@@

There are an almost limitless number of ways to define what the ``right''
clustering is. In this paper, we have considered one such notion---density upper
level sets---and have detailed a set of natural geometric criteria which, when 
appropriately satisfied, translate to provable bounds on estimation of the
cluster by PPR. We do not, however, provide theory to show that our geometric
conditions are required for successful recovery of a density level set. This
seems to be supported by our empirical results, and it remains a direction for 
future work.

@@

Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
\begin{corollary}
	\label{cor: appr}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$). Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
	\begin{enumerate}
		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
	\end{enumerate}
\end{corollary}

@@

\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}

The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$. We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$. All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.

@@

\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}

Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
\begin{equation*}
\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
\end{equation*}
and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
\begin{equation*}
\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
\end{equation*}

On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.

@@

\begin{lemma}
	\label{lem: soakage_ppr_lb}
	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
	\begin{equation*}
	\pbf_{v}(u) \leq \pbf_{s}(u)
	\end{equation*}
	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
\end{lemma}
\begin{proof}
	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
	\begin{align*}
	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
	& = \pbf_s(u)
	\end{align*}
\end{proof}

>>>>

\begin{theorem}
  \label{thm: consistent_recovery_of_density_clusters}
  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
  such that if  
  \begin{equation}
    \label{eqn: kappa_ub}
    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
  \end{equation}
  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
\end{theorem}
\noindent Some remarks are in order: 
 \begin{enumerate}  
 \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
  density cluster $\Cset$ in the sense of \eqref{eqn:
    consistent_density_cluster_recovery} only when we can guarantee a very small
  fraction of points will be misclassified. This strong condition is the price
  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
 \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
  behavior of PPR in this regime. Although the restriction to a kernel
  function fixed in $n$ is standard for spectral clustering theory
  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
  this is merely looseness in our upper bounds.  
\end{enumerate}
\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
changed this $\epsilon$ to $\varepsilon$.}

\subsection{Approximate PPR vector} 
In practice, exactly solving the system of equations~\eqref{eqn:
  ppr_vector} to compute the PPR vector 
  may be too computationally expensive. To address this limitation,
\citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
(aPPR), which we will denote by \smash{$\pbf^{(\varepsilon)}$}. We refer the
curious reader to \citet{andersen2006} for a formal algorithmic definition of
the aPPR vector, and limit ourselves to highlighting a few salient points: the
aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time,
while satisfying the following uniform error bound: 
\begin{equation}
\label{eqn: appr_error}
\textrm{for all $u \in V$}, \quad \pbf(u) - \varepsilon \Dbf_{uu}\leq
\pbf^{(\varepsilon)}(u) \leq \pbf(u).  
\end{equation}
For a sufficiently small choice of $\varepsilon$, the 
application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
formally state and prove this in Corollary~\ref{cor: appr} in 
Appendix~\ref{sec:appr}.

@@

\subsection{Upper Bound on the Normalized Cut} 
We start with a finite sample upper bound on the
normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
  $\epsilon > 0$, if 
  \begin{equation}
    \label{eqn: conductance_sample_complexity}
    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
  \end{equation}
  then with probability at least $1-\delta$, for a universal constant $c_1 > 0$,
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
  \end{equation}
\end{theorem}
\noindent {\bf Remark: } 
Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
    conductance_upper_bound}, in contrast to the condition number
  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This
  reflects established wisdom regarding spectral partitioning
  algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
  to the density clustering setting. It suggests that if the diameter $\rho$ is
  large, PPR may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is
  sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized
  cut in $G_{n,r}$. This intuition will be supported by simulations in Section
  \ref{sec: experiments}.

\subsection{Upper Bounds on the Mixing Time} 
For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
$\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write  
$$
q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
$$
for the $t$-step transition probability of the lazy random walk over $G[S]$
originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
for the stationary distribution of this random walk.  (As
$\Wbf_S$ is the transition matrix of a lazy random walk, 
it is well-known that a unique stationary distribution exists and is given by 
\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where we write $\Dbf_S$ for the  
degree matrix of $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
\begin{equation}
\label{eqn: mixing_time}
\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)}
  {\pi(u)} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}. 
\end{equation}
Next, we give an asymptotic (in the number of vertices $n$) upper bound on
$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.

@@

\vspace{0.2cm}

\noindent {\bf Remark: } 
  The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
  play an important role in proving the upper bound of Theorem \ref{thm:
    mixing_time_upper_bound}. There is some interdependence between $L$ and
  $\sigma,\rho$, which might lead one to hope that \ref{asmp: embedding} is
  non-essential. However, it is not possible to eliminate condition \ref{asmp:
    embedding} without incurring an additional factor of at least
  $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for
  instance, when $\Csig$ is a dumbbell-like set consisting of two balls of
  diameter $\rho$ linked by a cylinder of radius
  $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
  develop theory regarding bi-Lipschitz deformations of convex sets, wherein it
  is observed that star-shaped sets as well as half-moon shapes of the type we
  consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding}
  for reasonably small values of $L$.

@@

There are an almost limitless number of ways to define what the ``right''
clustering is. In this paper, we have considered one such notion---density upper
level sets---and have detailed a set of natural geometric criteria which, when 
appropriately satisfied, translate to provable bounds on estimation of the
cluster by PPR. We do not, however, provide theory to show that (some variant of) 
our geometric
conditions are \emph{required} for successful recovery of a density level set. This
seems to be supported by our empirical results, and establishing this necessity
formally is an important direction for 
future work.

@@

@@

@@

\subsection{The Approximate PPR Vector}
\label{sec:appr}
Before we proceed to the next section, we include a formal statement of our claims regarding the a\pprspace vector. 
\begin{corollary}
	\label{cor: appr}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$). Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
	\begin{enumerate}
		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
	\end{enumerate}
\end{corollary}
\begin{proof}
The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$. We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$. All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.

%\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}

Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
\begin{equation*}
\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
\end{equation*}
and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
\begin{equation*}
\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
\end{equation*}
On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.

@@

\begin{lemma}
	\label{lem: soakage_ppr_lb}
	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
	\begin{equation*}
	\pbf_{v}(u) \leq \pbf_{s}(u)
	\end{equation*}
	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
\end{lemma}
\begin{proof}
	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
	\begin{align*}
	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
	\end{align*}
	\begin{align*}
	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
	& = \pbf_s(u)
	\end{align*}
\end{proof}
